Endogenous Macrodynamics in Algorithmic Recourse

### 2023-01-23 paper/paper.tex
moved to publsihing site from docs folder instead of gh-pages

The findings for the other synthetic datasets are broadly consistent with the observations above. For the Moons data, the same broad patterns emerge, although in this case, the Greedy generator induces comparably strong shifts in some cases. For the Circles data, it also appears that Latent Space search yields better results. Model shifts and performance deterioration are also quantitatively smaller than what we can observe in Figure \ref{fig:syn}. For the Linearly Separable data we also find substantial domain and model shifts, but no reduction in model performance.\footnote{You can find a granular overview of all results including bootstraps in our online companion: \url{https://www.paltmeyer.com/endogenous-macrodynamics-in-algorithmic-recourse/}.}

>>>>

The findings for the other synthetic datasets are broadly consistent with the observations above. For the Moons data, the same broad patterns emerge, although in this case, the Greedy generator induces comparably strong shifts in some cases. For the Circles data, model shifts and performance deterioration are quantitatively much smaller than what we can observe in Figure \ref{fig:syn} and in many cases insignificant. For the Linearly Separable data we also find substantial domain and model shifts, but almost no reduction in model performance.\footnote{You can find a granular overview of all results including bootstraps in our online companion: \url{https://www.paltmeyer.com/endogenous-macrodynamics-in-algorithmic-recourse/}.}
